title: "planning awareness"
author: "Wangjio"
date: '2022-04-20'
output: pdf_document
---
header includes:
  - usepackage{hyperref}
  - usepackage

## R Markdown
```{r }
    x <- 1:10
    y <- round(rnorm(10, x, 1), 2)
    df <- data.frame(x, y)
    df
    ```
    ```{r basicconsole}
x <- 1:10
y <- round(rnorm(10, x, 1), 2)
df <- data.frame(x, y)
df
```

## Including Plots

### Simple plot

    ```{r }
    plot(DatasetTask)
    ```

```{r Frequency}
plot(DatasetTask)

### Multiple plots

    ```{r }
    boxplot(1:10~rep(1:2,5))
    plot(x, y)
    ```

```{r multipleplots}
boxplot(1:10~rep(1:2,5))
plot(x, y)
```
```

### `lattice` plot
As do lattice plots:

```{r latticeex}
xyplot(y~x)
```
 ```{r , results='asis', echo=FALSE}
    cat("Here are some dot points\n\n")
    cat(paste("* The value of y[", 1:3, "] is ", y[1:3], sep="", collapse="\n"))
    ```

```{r dotpointprint, results='asis', echo=FALSE}
cat("Here are some dot points\n\n")
cat(paste("* The value of y[", 1:3, "] is ", y[1:3], sep="", collapse="\n"))

### Create Markdown table code from R
    ```{r , results='asis', echo=FALSE}
    cat("x | y", "--- | ---", sep="\n")
    cat(apply(df, 1, function(X) paste(X, collapse=" | ")), sep = "\n")
    ```

```{r createtable, results='asis', echo=FALSE}
cat("x | y", "--- | ---", sep="\n")
cat(apply(df, 1, function(X) paste(X, collapse=" | ")), sep = "\n")
```

### Control output display
The folllowing code supresses display of R input commands (i.e., `echo=FALSE`)
and removes any preceding text from console output (`comment=""`; the default is `comment="##"`).


